Bird beak's elaboration and innovation

### 2021-11-04 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

---
title: "Bird beak's elaboration and exploration"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
bibliography: references.bib
output:
  html_document:
    fig_width: 8
    fig_height: 8
---

This section contains the code for reproducing the analyses. To get the details, refer to 03-elaboration_exploration_analyses.Rmd.

# Elaboration and exploration analyses

@@

```{r, message = FALSE, warning = FALSE, fig.height = 5, fig.width = 5, echo = FALSE}
## Plotting just the space
covar.plot(superorder_shapespace,
           main = "Shapespace",
           cex = 0.5,
           legend = FALSE)
```
The global Shape space

```{r, echo = FALSE, fig.height = 18, fig.width = 18, eval = TRUE}
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
## Plotting mean axes
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
```
Main axes and ellipses visualisation

## Calculate the elaborations/explorations

@@

```{r, echo = FALSE}
## Plot the results
wrap.plot <- function(results, col, main) {
    ## How many sub plots?
    n <- length(results)
    ## Edit names for cleaning
    # for(i in 1:n) {
    #     names(results[[i]]$disparity) <- gsub(":phylogeny", "", names(results[[i]]$disparity))
    # }

    ## Which will be the centre plot?
    centre <- 1
    ## Plot everything
    op <- par(mfrow = c(n, 1), mar = c(7, 4, 4, 2) + 0.1)
    for(i in 1:n) {
        plot(results[[i]], col = col, main = ifelse(i == centre, main, ""), las = 2, xlab = "")
    }
    par(op)
}
wrap.plot(results$super_results_between,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Superorders differences")
```
Figure: these results show the projections ("position"), rejection ("distance") and angles ("degree") of the posteriors of each group's major axes onto the corresponding global phylogenetic major axes. For each panel, the highest the score the more the clade is elaborating, exploring, exploring perpendicular to the main axes for the position, distance and degree respectively.

```{r, fig.height = 20, fig.width = 10, echo = FALSE}
wrap.plot(results$order_results_between,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Superorders differences")
```

## Elaboration and exploration by species

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}
## Plot the results
wrap.plot(results$super_results_phylo,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\non the global phylogeny axes")
```
Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.

```{r, fig.height = 20, fig.width = 10, echo = FALSE}

## Plot the results
wrap.plot(results$order_results_phylo,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\non the global phylogeny axes")
```

@@

```{r, fig.height = 20, fig.width = 10, echo = FALSE}

## Plot the results
wrap.plot(results$super_results_within,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "Projections per superorder\nonto each superorder")
```
Figure: the projection of each species per group onto the posterior distribution of each clade's major phylogenetic axis (the grey distributions corresponds to the projections of all the species, irregardless of their group, onto the global phylogenetic major axes).

```{r, fig.height = 20, fig.width = 10, echo = FALSE, eval = FALSE}

## Plot the results
wrap.plot(results$order_results_within,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "Projections per order\nonto each order")
```

## Different scores distributions per species

@@

#@param res the results list
#@param type which type (position, distance or angle)
#@param cent.tend which central tendency fun (default is median)
#@param use.hdr whether to use kernel density estimate for the outputs (default is TRUE)
#@param prob which quantiles to use (default is c(50, 95, 99))
#@param exclude.phylo remove the phylogeny subset (default = FALSE)
#@param ... plot options

get.distributions <- function(res, type, cent.tend = median, use.hdr = TRUE, prob = c(50, 95, 99), exclude.phylo = FALSE, ...) {

@@

    ## Recentre the results
    if(type == "position") {
        disparity <- lapply(disparity, function(X) return(X-0.5))
    }

@@

    return(output)
}
combine.results <- function(res1, res2) {
    ## Combine the results
    res_out <- rbind(res1[,1:2], res2[, 1:2])
    res_out$elaboration <- c(res1[, 3], rep(NA, nrow(res2)))
    res_out$exploration <- c(rep(NA, nrow(res1)), res2[, 3])
    ## Find any species in commons
    commons <- intersect(res1$species, res2$species)
    if(length(commons) > 0 && is.na(commons)) {
        if(is.na(res1$species)) {
            if(is.na(res2$species)) {
                ## Both are NA (keep just the first one)
                res_out <- res_out[-1, , drop = FALSE]
            } else {
                ## Remove res1
                res_out <- res_out[-1, , drop = FALSE]
            }
        } else {
            ## Remove res2
            res_out <- res_out[1:length(res1$species), , drop = FALSE]
        }
    } else {
        ## Recursively remove the ones in common
        while(length(commons) > 0) {
            duplicates <- which(res_out$species == commons[1])
            res_out[duplicates[1], 4] <- res_out[duplicates[2], 4]
            res_out <- res_out[-duplicates[2], ]
            commons <- commons[-1]
        }
    }
    return(res_out)
}
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_positions_phylo <- get.distributions(results$super_results_phylo, type = "position")
```
Figure: elaborations distributions per super orders

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_distances_phylo <- get.distributions(results$super_results_phylo, type = "distance")
```
Figure: explorations distributions per super orders

@@

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_distances_phylo <- get.distributions(results$order_results_phylo, type = "distance", exclude.phylo = TRUE)
```
Figure: explorations distributions per order

```{r, echo = FALSE}
## Combining the results
order_phylo_table <- do.call(rbind, mapply(combine.results, order_positions_phylo, order_distances_phylo, SIMPLIFY = FALSE))
rownames(order_phylo_table) <- NULL
kable(order_phylo_table, digits = 3)
```

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_distances_within <- get.distributions(results$super_results_within, type = "distance", exclude.phylo = TRUE)
```
Figure: explorations distributions within super orders

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_distances_within <- get.distributions(results$order_results_within, type = "distance", exclude.phylo = TRUE)
```
Figure: explorations distributions within orders

```{r, echo = FALSE}
## Combining the results
order_phylo_table_within <- do.call(rbind, mapply(combine.results, order_positions_within, order_distances_within, SIMPLIFY = FALSE))
rownames(order_phylo_table_within) <- NULL
kable(order_phylo_table_within, digits = 3)
```

## Correlations between elaboration and exploration?

```{r, echo = FALSE}
get.correlations <- function(res, cent.tend = median, exclude.phylo = FALSE, ...) {

@@

    ## Recentre the results
    disparity_pos <- lapply(disparity_pos, function(X) return(X-0.5))

@@

    ## Calculate and plot the hdrcde
    op_tmp <- par(mfrow = c(ceiling(sqrt(n_groups)), round(sqrt(n_groups))))
    for(i in 1:n_groups) {
        ## Testing the correlation
        cor_test <- cor.test(centrals_pos[[i]], centrals_dis[[i]])
        plot_main <- paste0(names(centrals_pos)[i], ": ", unname(round(cor_test$estimate, 3)), " (p=", unname(round(cor_test$p.value, 3)), ")")
        ## Plotting the results
        plot(centrals_pos[[i]], centrals_dis[[i]], pch = 19, xlab = "elaboration", ylab = "exploration", main = plot_main, cex = 0.5)
    }
    par(op_tmp)
    return(invisible())
}
```

>>>>

---
title: "Bird beak's elaboration and innovation"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
bibliography: references.bib
output:
  html_document:
    fig_width: 8
    fig_height: 8
---

This section contains the code for reproducing the analyses. To get the details, refer to 03-elaboration_innovation_analyses.Rmd.

@@

First we can visualise the global bird shape space (or at least the 2 first of the 8 dimensions):

```{r, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 8, echo = FALSE}
## Plotting just the space
covar.plot(superorder_shapespace,
           main = "Shapespace",
           cex = 0.5,
           legend = TRUE,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           legend.args = list(x = "bottomright", cex = 2/3))
```

Figure: The global shape space

We can then check the distribution of the variance covariance matrices for each super order and each order.
The VCV matrices are represented as average ellipses or average axis.

```{r, echo = FALSE, fig.height = 14, fig.width = 14, eval = TRUE}
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
## Plotting mean axes
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
```

Main axes and ellipses visualisation for each superorders and orders.

### Are these 2D average ellipses and/or axes an accurate representation of what's going on? 
<details>
  <summary>[Click to expand] TL;DR: It depends...
</summary>

A couple of things have to be taken into account:

 * First, the averaging of the VCV (and it's ellipse and/or maon axis) can result into weird "middle" VCV that are not representing the individual VCV (e.g. if half VCV are negative, and half positive, the average will be probably 0; which does not exist).
 * Second, the ellipses in nD projected onto a 2D space will be deformed (unless the VCV is a real pancake on the first 2D, i.e. with no variance on the other dimensions).

Note that both problems are only visual though since: 1) we don't use averages anywhere (but the full distributions all the time) and 2) the linear algebra bit with the projections and stuff works in any number of dimensions and transforms the results into 1D results (i.e. the projection/rejection of groups/species on the major axes in 8D space).

Here's a visualisation of how the variance in VCVs affects the averaging artefact:

```{r, eval = TRUE, echo = FALSE}
visualisation.group <- function(data, subset, dimensions, n = 100) {

    ## Get the subset
    sub <- get.subsets(data, subsets = subset)

    ## Make 2D
    if(!missing(dimensions)) {
        sub$matrix[[1]] <- sub$matrix[[1]][,dimensions]
        sub$call$dimensions <- dimensions
        fun2d <- function(covar) {
            covar$VCV <- covar$VCV[dimensions, dimensions]
            covar$loc <- covar$loc[dimensions]
            return(covar)
        }
        sub$covar <- lapply(sub$covar, lapply, fun2d)
        main_D <- "2D"
    } else {
        main_D <- "8D"
    }

    ## Make the tile
    main <- paste0(n, " random ", subset, " VCV (", main_D, ")")

    ## Plot
    covar.plot(sub, major.axes = TRUE, ellipses = TRUE, points = FALSE, legend = FALSE, main = main)
    covar.plot(sub, major.axes = mean, ellipses = mean, points = FALSE, col = "red", add = TRUE)
}

visualisation.group(superorder_shapespace, "Mirandornithes")
```

```{r, echo = FALSE, eval = TRUE}
visualisation.group(superorder_shapespace, "Strisores")
```

Or even more obvious (with an direction that does not really exist (due to averaging)):

```{r, echo = FALSE, eval = TRUE}
visualisation.group(superorder_shapespace, "Paleognathae")
```

For the 2Dness, the effect is a bit less obvious (because the two first dimensions already have so much variance). Here is an example for the Columbimorphae. (to check different groups, you can easily modify the source code of the Rmd. TODO: this would be good in some shiny app innovation thingy).

```{r, echo = FALSE, eval = TRUE, fig.height = 6, fig.width = 12}
par(mfrow = c(1,2))
visualisation.group(superorder_shapespace, "Columbimorphae")
visualisation.group(superorder_shapespace, "Columbimorphae", dimensions = c(1,2))
```

Back to the main story.
</details>

## Calculate the elaborations/innovations

We then calculate the projections/rejections as explained in more details in the [03-elaboration_exploration_analyses.Rmd]() script.
Really briefly we calculate three types of projections/rejections abbreviated as follows below:

 * `between`: the projection of each group's VCV (major axis) on the phylogenetic's VCV (major axis)
 * `phylo`: the projection of each element within a group (species) onto the phylogenetic's VCV (major axis)
 * `within`: the projection of each element within a group (species) onto its own VCV (major axis)

@@

### Projections between groups:

```{r, echo = FALSE, fig.height = 8, fig.width = 8}
## Plot the results
wrap.plot <- function(results, col, main, names, centre.position = TRUE, absolute = FALSE) {

    ## Adding one plot
    one.plot <- function(one_result, xlab, col, zero = TRUE, main, centre, absolute, ...) {
        values <- lapply(get.disparity(one_result, concatenate = FALSE), c)
        if(centre) {
            values <- lapply(values, function(X) {X-0.5})
        }
        if(absolute) {
            values <- lapply(values, function(X) {abs(X-0.5)})
        }
        boxplot(values, horizontal = TRUE, yaxt = "n", col = col, xlab = xlab, main = main, ...)
        if(zero) {
            abline(v = 0, col = "black", lty = 3, lwd = 1)
        }
    }

    ## How many sub plots?
    n <- length(results)

    ## Recycle labels?
    if(missing(names)) {
        names_list <-names(results)
    } else {
        names_list <- names
    }

    ## Which will be the centre plot?
    centre <- ceiling(n/2)
    ## Plot everything
    op <- par(mfrow = c(1, n+1))
    ## Plot the first panel
    par(bty = "n", mar = c(5, 14, 4, 0) + 0.1)
    empty <- matrix(0, ncol = length(results[[1]]$disparity))
    colnames(empty) <- names(results[[1]]$disparity)
    boxplot(empty, horizontal = TRUE, las = 2, col = "white", ylim = c(0,0), xaxt = "n", border = "white")
    for(i in 1:n) {
        ## Is position?
        is_position <- names(results)[[i]] == "position"
        par(mar = c(5, 0, 4, 0) + 0.1, bty = "o")
        one.plot(results[[i]], col = col, centre = is_position && centre.position, main = ifelse(i == centre, main, ""), xlab = names_list[i], zero = is_position, absolute = absolute)
    }
    par(op)
}
wrap.plot(results$super_results_between,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[between] superorders VCV\nonto the phylogenetic VCV",
          names = c("elaboration", "innovation", "angle"))
```

Figure: these results show the projections ("position"), rejection ("distance") and angles ("degree") of the posteriors of each group's major axes onto the corresponding global phylogenetic major axes. For each panel, the highest the score the more the clade is elaborating, exploring, exploring perpendicular to the main axes for the position, distance and degree respectively.

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 8, fig.width = 8}
wrap.plot(results$super_results_between,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[between] superorders VCV\nonto the phylogenetic VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

```{r, fig.height = 16, fig.width = 8, echo = FALSE}
wrap.plot(results$order_results_between,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[between] orders VCV\nonto the phylogenetic VCV",
          names = c("elaboration", "innovation", "angle"))
```

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 16, fig.width = 8}
wrap.plot(results$order_results_between,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[between] orders VCV\nonto the phylogenetic VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

### Projections of the species on the phylogenetic VCV

@@

```{r, fig.height = 8, fig.width = 8, echo = FALSE, eval = TRUE}
## Plot the results
wrap.plot(results$super_results_phylo,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[phylo] superorders species\nonto the phylogenetic VCV",
          names = c("elaboration", "innovation", "angle"))
```

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 8, fig.width = 8}
wrap.plot(results$super_results_phylo,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[phylo] superorders species\nonto the phylogenetic VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

Figure: the projection of each species per group onto the posterior distribution of global major phylogenetic axis.

```{r, fig.height = 16, fig.width = 8, echo = FALSE}

## Plot the results
wrap.plot(results$order_results_phylo,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[phylo] orders species\nonto the phylogenetic VCV",
          names = c("elaboration", "innovation", "angle"))
```

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 16, fig.width = 8}
wrap.plot(results$order_results_phylo,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[phylo] orders species\nonto the phylogenetic VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

### Projections of the species on their own group's VCV

@@

```{r, fig.height = 8, fig.width = 8, echo = FALSE}

## Plot the results
wrap.plot(results$super_results_within,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[within] superorders species\nonto their group's VCV",
          names = c("elaboration", "innovation", "angle"))
```

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 8, fig.width = 8}
wrap.plot(results$super_results_within,
          col = rainbow(n.subsets(superorder_shapespace)-1),
          main = "[within] superorders species\nonto their group's VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

Figure: the projection of each species per group onto the posterior distribution of each clade's major phylogenetic axis (the grey distributions corresponds to the projections of all the species, irregardless of their group, onto the global phylogenetic major axes).

```{r, fig.height = 16, fig.width = 8, echo = FALSE}

## Plot the results
wrap.plot(results$order_results_within,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[within] oreders species\nonto their group's VCV",
          names = c("elaboration", "innovation", "angle"))
```

<details>
  <summary>[Click to expand] The same but using absolute values for the projections (elaboration)
</summary>

```{r, echo = FALSE, fig.height = 16, fig.width = 8}
wrap.plot(results$order_results_within,
          col = rainbow(n.subsets(order_shapespace)-1),
          main = "[within] oreders species\nonto their group's VCV",
          names = c("absolute elaboration", "innovation", "angle"),
          centre.position = FALSE, absolute = TRUE)
```
</details>

So that's the story so far...

# Different scores distributions per species

@@

#@param res the results list
#@param type which type (position, distance or angle)
#@param cent.tend which central tendency fun (default is median)
#@param use.hdr whether to use kernel density estimate for the outputs (default is TRUE)
#@param prob which quantiles to use (default is c(50, 95, 99))
#@param exclude.phylo remove the phylogeny subset (default = FALSE)
#@param absolute whether to make the position values absolute or not
#@param ... plot options

get.distributions <- function(res, type, cent.tend = median, use.hdr = TRUE, prob = c(50, 95, 99), exclude.phylo = FALSE, absolute = FALSE, ...) {

@@

    ## Recentre the results
    if(type == "position") {
        if(!absolute) {
            disparity <- lapply(disparity, function(X) return(X-0.5))
        } else {
            disparity <- lapply(disparity, function(X) return(abs(X-0.5)))
        }
    }

@@

    return(output)
}
combine.results <- function(res1, res2) {
    ## Combine the results
    res_out <- rbind(res1[,1:2], res2[, 1:2])
    res_out$elaboration <- c(res1[, 3], rep(NA, nrow(res2)))
    res_out$innovation <- c(rep(NA, nrow(res1)), res2[, 3])
    ## Find any species in commons
    commons <- intersect(res1$species, res2$species)
    if(length(commons) > 0 && is.na(commons)) {
        if(is.na(res1$species)) {
            if(is.na(res2$species)) {
                ## Both are NA (keep just the first one)
                res_out <- res_out[-1, , drop = FALSE]
            } else {
                ## Remove res1
                res_out <- res_out[-1, , drop = FALSE]
            }
        } else {
            ## Remove res2
            res_out <- res_out[1:length(res1$species), , drop = FALSE]
        }
    } else {
        ## Recursively remove the ones in common
        while(length(commons) > 0) {
            duplicates <- which(res_out$species == commons[1])
            res_out[duplicates[1], 4] <- res_out[duplicates[2], 4]
            res_out <- res_out[-duplicates[2], ]
            commons <- commons[-1]
        }
    }
    return(res_out)
}
```

Furthermore, we can look at things species per species to find which species species have the most extreme values (in general, or within their groups).

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_positions_phylo <- get.distributions(results$super_results_phylo, type = "position", absolute = TRUE)
```
Figure: elaborations distributions per super orders

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_distances_phylo <- get.distributions(results$super_results_phylo, type = "distance")
```
Figure: innovations distributions per super orders

<details>
  <summary>[Click to expand] Table of species extreme values projected onto the phylogenetic VCV.
</summary>

@@

</details>

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_distances_phylo <- get.distributions(results$order_results_phylo, type = "distance", exclude.phylo = TRUE)
```
Figure: innovations distributions per order

<details>
  <summary>[Click to expand] Table of species extreme values projected onto their own group's VCV.
</summary>

```{r, echo = FALSE}
## Combining the results
order_phylo_table <- do.call(rbind, mapply(combine.results, order_positions_phylo, order_distances_phylo, SIMPLIFY = FALSE))
rownames(order_phylo_table) <- NULL
kable(order_phylo_table, digits = 3)
```
</details>

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
super_distances_within <- get.distributions(results$super_results_within, type = "distance", exclude.phylo = TRUE)
```
Figure: innovations distributions within super orders

<details>
  <summary>[Click to expand] Table of species extreme values projected onto their own group's VCV.
</summary>

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 12, fig.width = 12, eval = TRUE}
order_distances_within <- get.distributions(results$order_results_within, type = "distance", exclude.phylo = TRUE)
```
Figure: innovations distributions within orders

<details>
  <summary>[Click to expand] Table of species extreme values projected onto their own group's VCV.
</summary>

```{r, echo = FALSE}
## Combining the results
order_phylo_table_within <- do.call(rbind, mapply(combine.results, order_positions_within, order_distances_within, SIMPLIFY = FALSE))
rownames(order_phylo_table_within) <- NULL
kable(order_phylo_table_within, digits = 3)
```
</details>

## Correlations between elaboration and innovation?

```{r, echo = FALSE}
get.correlations <- function(res, cent.tend = median, exclude.phylo = FALSE, absolute = TRUE, ...) {

@@

    ## Recentre the results
    if(!absolute) {
        disparity_pos <- lapply(disparity_pos, function(X) return(X-0.5))
    } else {
        disparity_pos <- lapply(disparity_pos, function(X) return(abs(X-0.5)))
    }

@@

    ## Calculate and plot the hdrcde
    op_tmp <- par(mfrow = c(ceiling(sqrt(n_groups)), round(sqrt(n_groups))))
    for(i in 1:n_groups) {
        ## Testing the correlation
        cor_test <- cor.test(centrals_pos[[i]], centrals_dis[[i]])
        plot_main <- paste0(names(centrals_pos)[i], ": ", unname(round(cor_test$estimate, 3)), " (p=", unname(round(cor_test$p.value, 3)), ")")
        ## Plotting the results
        plot(centrals_pos[[i]], centrals_dis[[i]], pch = 19, xlab = "elaboration", ylab = "innovation", main = plot_main, cex = 0.5)
    }
    par(op_tmp)
    return(invisible())
}
```
